\section*{\underline{Projects and Academic Experience}}
\noindent \itbf{Diesel Engine Aftertreatment System Diagnostics} \hfill $August, 2023 - $ Ongoing
\begin{itemize}
        \item Created a Discrete nonlinear hybrid model for $NO_x$ process dynamics in diesel engine SCR-ASC system that captures the time-evolution of the measurement signals and predicts aging through parameter changes. Validated the model using real-world test-cell and truck data.
        \item Developed a framework for aging diagnostics using set-membership filtering and parameter change detection.
\end{itemize}

%===
\medskip
%===

\noindent \itbf{Actuator Fault diagnosis and robust control in Multi-rotors using RPM feedback} \hfill $August, 2021 - $ Ongoing
\begin{itemize}
        \item Developed an RPM measurement system using the back-emf commutation signals from the BLDC motor.
        \item Formulated and identified nonlinear model that accommodates the input uncertainties due to unknown high-frequency filters inside the ESC (ACC, 2024).
        \item Demonstrated the effectiveness of Adaptive Robust Control for uncertainty rejection and RPM tracking under parameter fluctuations and faults (MECC, 2024).
        \item Developed a framework for fault-diagnostics and reconfiguration using Set-membership filtering and adaptive robust control.
\end{itemize}

%===
\medskip
%===

\noindent \itbf{Instructor/TA for Control Lab Courses} \hfill $August, 2020 - May, 2023$
\begin{itemize}
%        \item Teaching Assistant for graduate laboratory courses on Mechatronics (ME 588) and Microprocessors and
%        Electromechanical Systems (ME 586) and undergraduate laboratory courses in Measurement and Control (ME 375, ME
%        365, AAE 364, AAE 421).

        \item Assisted students in writing C, Assembly and LabView programs, and their debugging for developing closed loop control for mechanical systems such as inverted pendulum, DC motor and, heating and cooling systems using STM32 or NI-MyRio.

        \item \itbf{Course Development:} Demonstrated parameter estimation and robust control implementation procedures for refrigeration system with variable speed compressor and flow control valve (non-minimum phase system) using STM32 Discovery board as possible guided final project for the future course offerings of ME 586.
\end{itemize}
%===
\medskip
%===
\itbf{Relevant Course Work:} Vehicle Dynamics, Multivariable Systems and Robust Control, Adaptive Control, Detection \& Estimation Theory, System Identification, Computational Statistics (EM algorithm), Reinforcement Learning (Bandit problems and MDPs) and Nonlinear Systems.

Relevant course projects include:
\begin{itemize}
        \item Nonlinear steering and breaking control considering roll-steer coupling for roll-over avoidance.
        \item $\mu$-synthesis based active suspension design for quarter and half-car model considering the Olley ride criteria.
\end{itemize}

% ======================================================================================================================
\noindent\rule{\textwidth}{0.4pt}
