\section*{\underline{Work Experience}}
% ======================================================================================================================
\noindent \textit{System Analyst Intern (Robotic Algorithms and Controls)}

\textbf{Intuitive Surgical} - Sunnyvale, California \hfill $June, 2025  - August, 2025$

\begin{itemize}
        \item Worked on fault diagnostics for motors in haptics of surgeon side console resulting in a new invention disclosure.
        \begin{itemize}
                \item Implemented tools for detecting the new fault in the motors from the field data.
                \item Developed and experimentally validated the analytical model of the motor operation under the newly diagnosed fault.
                \item Developed the relationship between the residual and torque loss due to fault for validating thresholds.
        \end{itemize}
        \item Proposed a spec change for hall sensors in a motor by validating it against motor safety algorithms and other specs on the same sensors that doubled the manufacturing process capability metric.
\end{itemize}
% ======================================================================================================================

\medskip


% ======================================================================================================================
\noindent \textit{Motion Control Engineer } (Internship)

\textbf{Virgin Hyperloop} - Los Angeles, California \hfill $June, 2022  - August, 2022$

\begin{itemize}
        \item Designed and demonstrated supervisory control to minimize force mismatch across bogies, improving EM engine efficiency.
        \item Refined control architecture for EM engine using MATLAB/Simulink, demonstrating linear control limitations. Explored implementation of field oriented control (FOC) of the PMSM drive for bogie propulsion.
        \item Developed a MIMO model for guidance bogie engine assembly and analyzed robust stability and control performance w.r.t suspension parameters.
\end{itemize}
% ======================================================================================================================

\medskip

% ======================================================================================================================
\noindent\textit{Research Engineer  - Estimation and Control Systems} (Internship)

\textbf{SC Solutions} - Portland, Oregon \hfill $May, 2023 - August, 2023$

\begin{itemize}
    \item Developed auto-regressive estimation models for computer vision-based fat estimation in meat (USDA-funded project).
    \item Designed state and parameter estimation algorithms using vision data; implemented OpenCV-based real-time estimation software in C++.
\end{itemize}
% ======================================================================================================================

\medskip

% ======================================================================================================================
\noindent\textit{Scientist/Engineer 'SC', Test Instrumentation and Controls, Thermal Systems Group} (Full-time role)

\textbf{Indian Space Research Organization (ISRO)} - Bengaluru, India \hfill $July, 2016 - July, 2019$

\begin{itemize}
        \item Led thermal instrumentation and control for 15 satellite systems, including Chandrayaan-2 (orbiter, lander, rover).
        \item Developed a Python-based SCADA interface, doubling satellite test productivity and enabling simultaneous testing.
	\item Designed an optimal heater control and design tool with a web-based front-end, preventing burnout and saturation faults.
        \item Demonstrated the use of the EPICS framework on a test setup as a proof of concept for a unified SCADA
                system, as part of the proposed technology development program.
\end{itemize}
% ======================================================================================================================
\noindent\rule{\textwidth}{0.4pt}
